Planetary perturbers, or: flaring star-planet interactions in Kepler and TESS

### 2023-06-23 src/tex/ms.tex
[showyourwork] overleaf sync

\begin{figure*}[ht!]
\script{paper_illustrative_sketch_of_system_geometries.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/system_geometries.png}
        \caption{
         Simplified magnetic star-planet interaction (SPI) geometries.\textbf{ Panel a: Fully aligned system along the line of sight (LOS). }Magnetic, rotational, and orbital axis are aligned. The interaction footpoint moves along the black line, and is visible to the observer on the red line, i.e. during $50\%$ of the planet's orbit. Flares induced along this line will result in excess flares when the planet is in front of the star. \textbf{Panel b: Orbital misalignment.} Same a panel a., but the planet's orbit is misaligned. The footpoint of interaction is again visible $50\%$ of the time, resulting in modulated flaring with orbital phase. However, it passes different latitudes on the star, which correspond to different dipole field strengths and coronal regions, which may affect the power of interaction. \textbf{Panel c: Inclined fully aligned system.} The red interaction footpoint line is visible $100\%$ of the time. No modulation due to magnetic SPI can be observed, even if flares are triggered by the planet. The sketches only show the interaction on one hemisphere of the star, but they may appear on both.
        }
        \label{fig:sketch}
    \end{centering}
\end{figure*}

>>>>

\begin{figure*}[ht!]
\script{paper_illustrative_sketch_of_system_geometries.py}
    \begin{centering}
        \includegraphics[width=0.8\linewidth]{figures/system_geometries.png}
        \caption{
         Simplified magnetic star-planet interaction (SPI) viewing geometries. The hatched hemisphere is visible to the observer. \textbf{ Panel a: Fully aligned system along the line of sight (LOS). } Magnetic, rotational, and orbital axis are aligned. The interaction footpoint moves along the black line, and is visible to the observer on the red latitude, i.e. during $50\%$ of the planet's orbit. Flares induced along this latitude will result in excess flares when the planet is in front of the star \textbf{Panel b: Inclined fully aligned system.} The interaction footpoint latitude is visible $100\%$ of the time. No modulation due to magnetic SPI can be observed, even if flares are triggered by the planet. The sketches only show the interaction on one hemisphere of the star, but they may appear on both. More complicated geometries arise when orbital, rotational and magnetic axis are mutually misaligned. The two panels also illustrate how a planet in a closer orbit interacts at a lower latitude than a farther out planet. }
        \label{fig:sketch}
    \end{centering}
\end{figure*}
